\documentclass[10pt, letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\pagestyle{empty}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{PRAFUL SHRESTHA}} \\ \vspace{4pt}
    +4571529960 | sthpraful19@gmail.com | Github
\end{center}

% --- SUMMARY ---
\section{Professional Summary}
Highly analytical and detail-oriented MSc Business Data Science student with a strong foundation in data processing, analysis, and visualization, eager to apply and expand skills in a mission-driven environment. Proficient in Excel, Python, and advanced data tools, with a proven ability to quickly learn and master new technologies. Passionate about leveraging data to drive informed decisions and committed to contributing to a supportive, collaborative team focused on making a real impact for children. Eager to develop expertise in Power BI for dashboard creation and Microsoft Dynamics 365 for CRM data management, building on existing experience with data quality assurance and system operations.

% --- SKILLS ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Core Competencies:} Data Analysis \& Processing: Python (Pandas, NumPy, Scikit-learn), Excel, Data Cleaning, Data Quality Assurance, Statistical Analysis, Data Segmentation, Data Visualization: Matplotlib, Seaborn, Eager to learn Power BI for dashboard development, Machine Learning \& AI: LLM-based extraction, Prompt Engineering, Text Classification, Topic Modeling (BERTopic), QLoRA, Systems \& Tools: CRM systems (BrokerEngine, eager to learn Microsoft Dynamics 365), Jupyter Notebook, Visual Studio Code, Git, UCloud, AAU AI-LAB, GPU Compute, Core Competencies: Analytical Thinking, Problem Solving, Detail-Oriented, Systematic Work, Quality-Conscious, Solution-Oriented, Independent Work, Proactivity, Communication
\end{itemize}

% --- PROJECTS ---
\section{Technical \& Data Projects}
\noindent\textbf{AI Detection \& Topic Modeling of Danish News Articles (1.2M+ articles)} \hfill \textit{Relevant Project}\\
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Processed and cleaned over 1.2 million Danish news articles using Pandas and parallel chunk-based batch processing within a high-performance computing environment, ensuring data readiness for analysis.
    \item Implemented zero-shot and few-shot text classification techniques with multilingual NLI models to categorize diverse topics and accurately detect AI-generated content, providing insights for market research.
    \item Applied BERTopic modeling to uncover latent discourse themes and visualize insights, enhancing interpretability for data-driven decision-making.
\end{itemize}
\vspace{4pt}
\noindent\textbf{LLM-Based Risk Analysis of S\&P 500 Earnings Calls} \hfill \textit{Relevant Project}\\
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Engineered an LLM-powered pipeline to extract structured corporate risk data from S\&P 500 earnings call transcripts, transforming unstructured text into actionable insights for financial analysis.
    \item Designed a strict JSON schema using Pydantic and enforced structured outputs via advanced prompt engineering, ensuring data consistency and reliability for downstream reporting.
    \item Constructed a company-risk bipartite knowledge graph using NetworkX to visualize systemic market risks across varying sectors, providing a clear overview of interdependencies and potential vulnerabilities.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Multi-Agent ESG Patent Classification System} \hfill \textit{Relevant Project}\\
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Architected an autonomous multi-agent AI system, leveraging advocate, skeptic, and judge personas to systematically evaluate and debate technical documents for ESG compliance, enhancing classification accuracy and data quality.
    \item Fine-tuned a foundational LLM using QLoRA on a GPU-accelerated cluster, optimizing its performance as the specialized 'brain' for complex data classification tasks.
    \item Successfully deployed the multi-agent debate workflow to accurately classify patents under the Y02 climate change mitigation category, automating complex market research and improving efficiency.
\end{itemize}
\vspace{4pt}


% --- EXPERIENCE ---
\section{Work Experience}
\noindent\textbf{Relationship Associate} $|$ \textit{SmartMove Nepal} \hfill Apr 2024-Jul 2024\\
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Supported Mortgage Advisors in managing client relationships and streamlining loan applications, contributing to efficient client service delivery and data collection.
    \item Acted as a crucial liaison between clients, banks, and internal teams, ensuring seamless communication and providing timely updates on loan statuses.
    \item Collected and meticulously organized required client documents based on specific loan types, ensuring compliance and completeness for system operations and data quality.
    \item Conducted thorough loan eligibility research and requested pricing options from various banks, optimizing loan matching for clients through systematic data comparison.
    \item Prepared detailed product comparisons in Excel and 'BrokerWizard' to assist clients in making informed decisions and choosing suitable loan options, supporting data-based recommendations.
    \item Built comprehensive loan applications in 'BrokerWizard' and coordinated their submission, ensuring a smooth application process and accurate data entry.
    \item Monitored loan approval statuses, uploaded additional documents, and maintained proactive communication with banks to expedite approvals, contributing to efficient data flow.
    \item Utilized a suite of tools including 'BrokerEngine' (CRM), 'Quickly', 'Flex', and Excel for efficient client servicing and comprehensive loan processing, demonstrating strong system navigation skills.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Accountant} $|$ \textit{Sajo Packaging Industry Pvt. Ltd.} \hfill Dec 2022-May 2023\\
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Maintained accurate financial records and ensured strict compliance with VAT regulations, contributing to financial integrity and data quality.
    \item Managed payroll processing efficiently and prepared comprehensive monthly financial statements, providing clear insights into company performance and key figures.
    \item Assisted in pricing strategies and conducted diligent expense monitoring, supporting cost-effective business operations through data analysis.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Intern} $|$ \textit{Nepal Bank Limited} \hfill Mar 2022-May 2022\\
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Supported various loan processing and customer service activities, gaining practical experience in banking operations and data handling.
    \item Maintained daily records of banking activities, including tracking bank expenses, managing account openings, and ensuring accurate documentation in registers, emphasizing systematic data entry.
    \item Gained hands-on experience in core banking operations, enhancing understanding of financial services data.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Intern} $|$ \textit{Jawalakhel Group of Industries} \hfill May 2017-Aug 2017\\
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Used Excel to accurately input, manage, and organize diverse datasets, contributing to efficient data management.
    \item Ensured data accuracy by performing rigorous quality checks, maintaining high standards of data integrity.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Receptionist} $|$ \textit{Nepal Mastermind} \hfill Apr 2015-May 2017\\
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Managed front-desk operations efficiently, serving as the primary point of contact for clients and visitors.
    \item Created bills for program enrollees, tracked expenses, and maintained meticulous records of incoming payments, ensuring financial transparency and systematic data organization.
    \item Ensured accurate documentation and facilitated smooth communication between clients and the administrative team, enhancing operational flow and data accuracy.
\end{itemize}
\vspace{4pt}


% --- EDUCATION ---
\section{Education}
\noindent\textbf{Aalborg University} \hfill Sep 2023-Ongoing\\
\textit{MSc Business Data Science}\\
\vspace{2pt}

\noindent\textbf{Bhaktapur Multiple Campus} \hfill Aug 2017–Jul 2022\\
\textit{Bachelor of Business Administration}\\
\vspace{2pt}



\end{document}