\documentclass[10pt, letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\pagestyle{empty}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{PRAFUL SHRESTHA}} \\ \vspace{4pt}
    +4571529960 | sthpraful19@gmail.com | Github
\end{center}

% --- SUMMARY ---
\section{Professional Summary}
Highly analytical and detail-oriented Master's student in Business Data Science with a strong foundation in data processing, analysis, and insight generation from large datasets. Proficient in Python, Pandas, and advanced LLM techniques, complemented by practical experience in data structuring, reporting, and database management. Eager to apply strong analytical reasoning and problem-solving skills to contribute to data-driven decision-making, with proven capabilities in SQL, PowerBI, and DBT for building and maintaining robust data solutions and reports.

% --- SKILLS ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-2pt]
    \item \textbf{Data Analysis \& Tools:} Python (Pandas, NumPy, Scikit-learn), SQL, PowerBI, DBT, Excel, Jupyter Notebook, Visual Studio Code, Git
    \item \textbf{Machine Learning \& LLMs:} PyTorch, HuggingFace Transformers, LLM-based extraction, Prompt Engineering, QLoRA, BERTopic, Text Classification, Ollama, RNNs
    \item \textbf{Data Management \& Platforms:} Parquet, UCloud, AAU AI-LAB, GPU Compute, CRM systems
    \item \textbf{Languages:} English, Japanese, Hindi, Nepali, Newa Bhasa

\end{itemize}

% --- PROJECTS ---
\section{Technical \& Data Projects}
\noindent\textbf{Multi-Agent ESG Patent Classification System}
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Architected an autonomous multi-agent AI system, leveraging distinct advocate, skeptic, and judge personas to rigorously evaluate and debate technical documents for ESG compliance, enhancing classification accuracy.
    \item Fine-tuned a foundational Large Language Model (LLM) using QLoRA (Parameter-Efficient Fine-Tuning) on Aalborg University's GPU-accelerated AI-LAB cluster, optimizing its performance to serve as the specialized 'brain' for the advocate agent.
    \item Successfully deployed the multi-agent debate workflow to accurately classify patents under the Y02 climate change mitigation category, significantly automating complex market research and improving efficiency.
\end{itemize}
\vspace{4pt}
\noindent\textbf{AI Detection \& Topic Modeling of Danish News Articles (1.2M+ articles)}
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Processed and cleaned over 1.2 million Danish news articles using Pandas for data manipulation, Parquet optimization for efficient storage, and parallel chunk-based batch processing within a high-performance computing environment, preparing data for downstream analysis and reporting.
    \item Implemented advanced zero-shot and few-shot text classification techniques utilizing multilingual NLI models to categorize diverse topics and accurately detect AI-generated content within the large dataset.
    \item Applied BERTopic modeling with E5 sentence embeddings, UMAP for dimensionality reduction, and HDBSCAN for robust clustering to uncover latent discourse themes, visualizing insights for enhanced interpretability and understanding.
\end{itemize}
\vspace{4pt}
\noindent\textbf{LLM-Based Risk Analysis of S\&P 500 Earnings Calls}
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Engineered an LLM-powered pipeline to extract structured corporate risk data from extensive earnings call transcripts, transforming unstructured text into actionable insights suitable for database integration and reporting.
    \item Designed a strict JSON schema using Pydantic and enforced structured outputs via precise prompt engineering, ensuring data consistency and reliability for downstream analysis and PowerBI dashboards.
    \item Constructed a company-risk bipartite knowledge graph using NetworkX to visualize systemic market risks across varying sectors, providing a clear overview of interdependencies and potential vulnerabilities.
\end{itemize}
\vspace{4pt}


% --- EXPERIENCE ---
\section{Work Experience}
\noindent\textbf{Relationship Associate} $|$ \textit{SmartMove Nepal} \hfill Apr 2025 - Jul 2025
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Supported Mortgage Advisors in managing client relationships and streamlining loan applications, contributing to efficient client service delivery.
    \item Acted as a crucial liaison between clients, banks, and internal teams, ensuring smooth communication and providing timely updates on loan statuses.
    \item Collected and organized all required client documents meticulously based on specific loan types (refinance, pre-approval, investment, or owner-occupied), ensuring compliance and completeness for data-driven processing.
    \item Conducted thorough loan eligibility research using 'Quickly' and requested pricing options from various banks via their dedicated portals and 'Flex', optimizing loan product selection through systematic data comparison.
    \item Prepared detailed product comparisons in Excel and 'BrokerWizard' to assist clients in choosing the most suitable loan options tailored to their financial needs, demonstrating data presentation skills.
    \item Built comprehensive loan applications in 'BrokerWizard' and coordinated their submission through 'BrokerEngine' to operations and banks, ensuring a seamless application process and accurate data transfer.
    \item Monitored loan approval status, uploaded additional documents in 'Flex/FMS' as required, and maintained smooth communication with banks to expedite approvals, managing data flow efficiently.
    \item Utilized a suite of tools including 'BrokerEngine' (CRM), 'Quickly', 'Flex', 'LastPass', and Excel for efficient client servicing and comprehensive loan processing, handling diverse data inputs.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Accountant} $|$ \textit{Sajo Packaging Industry Pvt. Ltd.} \hfill Dec 2022 - May 2023
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Maintained accurate financial records and ensured strict compliance with VAT regulations, utilizing structured data practices.
    \item Managed payroll processing for all employees and prepared monthly financial statements, providing critical insights into the company's financial performance through clear reporting.
    \item Assisted in pricing strategies and conducted expense monitoring, contributing to cost control and profitability analysis based on financial data.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Intern} $|$ \textit{Nepal Bank Limited} \hfill Mar 2022 - May 2022
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Supported various loan processing and customer service activities, gaining practical experience in banking operations and data handling.
    \item Maintained daily records of banking activities, including tracking bank expenses, managing account openings, and ensuring accurate documentation in registers, demonstrating meticulous data entry and organization.
    \item Gained hands-on experience in core banking operations, enhancing understanding of financial services and customer interaction.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Intern} $|$ \textit{Jawalakhel Group of Industries} \hfill May 2017 - Aug 2017
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Utilized Excel to accurately input, manage, and organize diverse datasets, contributing to efficient data handling and preparation for analysis.
    \item Ensured data accuracy by performing rigorous quality checks, maintaining high standards of data integrity for business operations and reporting.
\end{itemize}
\vspace{4pt}
\noindent\textbf{Receptionist} $|$ \textit{Nepal Mastermind} \hfill Apr 2015 - May 2017
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Managed all front-desk operations, serving as the primary point of contact for clients and visitors, and meticulously tracking client interactions.
    \item Created bills for program enrollees, tracked expenses, and maintained meticulous records of incoming payments, ensuring financial transparency and accurate data logging.
    \item Ensured accurate documentation and facilitated smooth communication between clients and the administrative team, enhancing operational efficiency and client satisfaction.
\end{itemize}
\vspace{4pt}


% --- EDUCATION ---
\section{Education}
\noindent\textbf{Aalborg University} \hfill Sep 2025 - Ongoing\\
\textit{MSc Business Data Science}\\
\vspace{2pt}

\noindent\textbf{Bhaktapur Multiple Campus} \hfill Aug 2017 – Jul 2022\\
\textit{Bachelor of Business Administration}\\
\vspace{2pt}



\end{document}