\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{parskip} % This handles paragraph spacing perfectly on its own
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\noindent Dear Hiring Team,

I hope you are well.

Renewable energy markets move fast. If your pricing models don't capture every subtle shift in asset performance or market risk, you leave significant value on the table. The challenge lies in extracting real-time, actionable insights from vast, unstructured data to make informed commercial decisions.

Many companies struggle to turn unstructured text from earnings calls into structured, actionable risk data, leading to blind spots in market assessments. I engineered an LLM-powered pipeline that automatically extracted structured corporate risk data from these transcripts. I designed a strict JSON schema with Pydantic and used precise prompt engineering to ensure accurate outputs. Then, I built a company-risk bipartite knowledge graph using NetworkX. This system visualized systemic market risks across various sectors, providing clear, data-driven insights previously hidden in raw text.

Analyzing over a million Danish news articles for AI detection and latent discourse themes presented a massive data processing challenge. I processed and cleaned all 1.2 million articles using Pandas, Parquet optimization, and parallel chunk-based batch processing in a high-performance computing environment. I then applied BERTopic modeling with advanced embeddings to uncover hidden themes. This allowed accurate categorization of topics and detection of AI-generated content, transforming raw data into interpretable insights crucial for complex market analysis.

My experience building robust data pipelines, extracting critical insights, and developing analytical tools in Python directly aligns with your need for precise pricing methodologies and risk assessments. I am eager to apply my data science expertise to help drive your commercial success in the renewable energy sector.

\vspace{2em}
\noindent Kindest Regards,\\
\textbf{PRAFULSHRESTHA}

\end{document}