\documentclass[10pt, letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\pagestyle{empty}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{PRAFULSHRESTHA}} \\ \vspace{4pt}
    +4571529960 $|$ \href{mailto:sthpraful19@gmail.com}{sthpraful19@gmail.com} $|$ \href{https://https://github.com/xprafulx}{GitHub}
\end{center}

% --- SUMMARY ---
\section{Professional Summary}
Business Data Science student at Aalborg University with a strong foundation in AI/ML, quantitative analysis, and market dynamics. Eager to apply advanced data science techniques to optimize pricing strategies, inform commercial decisions, and assess market risks, particularly within the renewable energy sector. Proven ability to translate complex technical models into actionable insights for strategic business outcomes.

% --- SKILLS ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-2pt]
    \item \textbf{Programming \& Data Science:} Python, Pandas, NumPy, Scikit-learn, PyTorch, HuggingFace Transformers, LLM-based Extraction, Prompt Engineering, Pydantic, Topic Modeling (BERTopic), Text Classification, NetworkX, Ollama, QLoRA, RNNs
    \item \textbf{Data Visualization \& Analysis:} Matplotlib, Seaborn, Excel
    \item \textbf{Tools \& Platforms:} Jupyter Notebook, Visual Studio Code, Git, UCloud, AAU AI-LAB, GPU Compute, CRM Systems
    \item \textbf{Languages:} English, Japanese, Hindi, Nepali, Newa Bhasa

\end{itemize}

% --- DYNAMIC SECTIONS (Experience, Projects, Certs, etc.) ---
\section{TECHNICAL \& BUSINESS DATA PROJECTS}
\noindent\textbf{Multi-Agent ESG Patent Classification System} \hfill 
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Developed an autonomous multi-agent AI system to evaluate technical documents for ESG compliance, demonstrating advanced analytical capabilities relevant to market valuation and risk assessment.
    \item Utilized QLoRA for fine-tuning a foundational LLM on Aalborg University's GPU-accelerated AI-LAB, enhancing its ability to process complex information for commercial insights.
    \item Automated complex market research for patent classification, providing a framework for data-driven commercial decision-making.
\end{itemize}
\vspace{4pt}

\noindent\textbf{AI Detection \& Topic Modeling of Danish News Articles (1.2M+ articles)} \hfill 
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Analyzed over 1.2 million news articles, applying advanced data processing and text classification techniques to identify market trends and sentiment.
    \item Utilized BERTopic modeling to uncover latent discourse themes, providing insights crucial for understanding market dynamics and informing commercial strategies.
    \item Demonstrated proficiency in handling large datasets and extracting actionable intelligence for strategic decision-making.
\end{itemize}
\vspace{4pt}

\noindent\textbf{LLM-Based Risk Analysis of S\&P 500 Earnings Calls} \hfill 
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Engineered an LLM-powered pipeline to extract structured corporate risk data from S\&P 500 earnings calls, directly applicable to financial risk assessment and pricing models.
    \item Designed a strict JSON schema and enforced structured outputs to ensure data quality for quantitative analysis.
    \item Constructed a company-risk knowledge graph to visualize systemic market risks, providing a robust framework for understanding market dynamics and informing pricing strategies.
\end{itemize}
\vspace{4pt}

\section{WORK EXPERIENCE}
\noindent\textbf{Relationship Associate} $|$ \textit{SmartMove Nepal} \hfill Apr2025-Jul2025
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Supported mortgage advisors by conducting loan eligibility research and actively requesting and comparing pricing options from various banks.
    \item Prepared detailed product comparisons in Excel to inform client decision-making on loan options, directly contributing to commercial outcomes.
    \item Monitored loan approval status and managed property valuations, demonstrating a practical understanding of financial product pricing and market dynamics.
    \item Utilized CRM systems and Excel for efficient client servicing and loan processing, ensuring data accuracy and operational efficiency.
\end{itemize}
\vspace{4pt}

\noindent\textbf{Accountant} $|$ \textit{Sajo Packaging Industry Pvt. Ltd.} \hfill Dec2022-May2023
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Maintained accurate financial records and assisted in pricing and expense monitoring, contributing to cost analysis and commercial decision-making.
    \item Managed payroll and prepared monthly financial statements, ensuring compliance and supporting financial transparency.
\end{itemize}
\vspace{4pt}

\noindent\textbf{Intern} $|$ \textit{Nepal Bank Limited} \hfill Mar2022-May2022
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Supported loan processing and maintained daily records of banking activities, gaining hands-on experience in financial operations and data management.
    \item Ensured accurate documentation and tracking of bank expenses, contributing to operational oversight.
\end{itemize}
\vspace{4pt}

\noindent\textbf{Intern} $|$ \textit{Jawalakhel Group of Industries} \hfill May2017-Aug2017
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Utilized Excel for accurate data input, management, and organization, performing quality checks to ensure data integrity for business analysis.
\end{itemize}
\vspace{4pt}

\noindent\textbf{Receptionist} $|$ \textit{Nepal Mastermind} \hfill Apr2015-May2017
\begin{itemize}[leftmargin=0.15in, topsep=0pt, partopsep=0pt, itemsep=-2pt]
    \item Managed front-desk operations, including creating bills and tracking expenses and payments, demonstrating attention to detail in financial record-keeping and client interactions.
\end{itemize}
\vspace{4pt}

\section{CERTIFICATIONS}
\noindent\textbf{Intro \& Intermediate Python} $|$ \textit{DataCamp} \hfill 2025
\vspace{4pt}

\noindent\textbf{Technical Analysis} $|$ \textit{NCITrading} \hfill 2023
\vspace{4pt}



% --- EDUCATION ---
\section{Education}
\noindent\textbf{Economics and Business Administration/MSc Business Data Science} $|$ \textit{Aalborg University} \hfill Sep2025-Ongoing\\
\vspace{2pt}

\noindent\textbf{Bachelor of Business Administration} $|$ \textit{Bhaktapur Multiple Campus.} \hfill Aug2017–Jul2022\\
\vspace{2pt}



\end{document}